2H qSIP Calculations

### 2021-09-09 qSIP_calculations.Rmd
Update qSIP_calculations.Rmd

---
title: "2H qSIP Calculations"
author: "Tristan Caro"
date: "`r Sys.Date()`"
  html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

@@

```{r}
p_gen_time_dist <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = gen_d, 
      y = inc_time_d_str, 
      color = inc_time_d_str, 
      fill = inc_time_d_str)) +
  stat_slab(height = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  geom_point(
    color = "black",
    shape = 124,
    size = 3,
    alpha = 1,
    position = position_nudge(y = .03)) +
  geom_text_repel(aes(label = compound), 
                  color = "black", 
                  nudge_y = -0.3, 
                  size = 3) +
  scale_x_log10() +
  annotation_logticks(sides = "b") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(x = "Generation time (days)",
       y = "Incubation time",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria collected from Alpine Tundra",
       caption = "Soils collected from Niwot Ridge LTER") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank())

ggsave("fig_output/p_gen_times_dist.png", plot = p_gen_time_dist, height = 6, width = 8, dpi = 300)
```

@@

### IRMS relabund
```{r}
peaks_mapped_active %>% ggplot(aes(x = rt, y = rel_amount, color = inc_time_d_str)) +
  geom_col() +
  facet_wrap(~inc_time_d_str, ncol = 1)
```

### Relabund vs. activity
```{r}
gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = rel_amount, y = u_d, color = inc_time_d_str, label = compound)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE) +
  geom_text_repel(size = 3) +
  scale_color_npg()
```

>>>>

---
title: "2H qSIP Calculations"
author: "Tristan Caro"
date: "`r Sys.Date()`"
output:
    html_document:
    code_folding: show
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options:
  chunk_output_type: console
---

@@

```{r}
p_gen_time_dist <- gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = gen_d, 
      y = inc_time_d_str, 
      color = inc_time_d_str, 
      fill = inc_time_d_str)) +
  stat_slab(height = 0.3, alpha = 0.7) +
  stat_pointinterval(color = "black") +
  geom_point(
    color = "black",
    shape = 124,
    size = 3,
    alpha = 1,
    position = position_nudge(y = .03)) +
  geom_text_repel(aes(label = compound), 
                  color = "black", 
                  nudge_y = -0.3, 
                  size = 3) +
  scale_x_log10() +
  annotation_logticks(sides = "b") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(x = "Generation time (days)",
       y = "Incubation time",
       title = "Generation times of soil bacteria",
       subtitle = "Lipid-specific generation times of bacteria collected from Alpine Tundra",
       caption = "Soils collected from Niwot Ridge LTER") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
p_gen_time_dist

#ggsave("fig_output/p_gen_times_dist.png", plot = p_gen_time_dist, height = 6, width = 8, dpi = 300)
```

@@

### IRMS relabund
```{r}
peaks_mapped_active %>% ggplot(aes(x = rt, y = rel_amount, fill = inc_time_d_str, color = inc_time_d_str)) +
  geom_col() +
  facet_wrap(~inc_time_d_str, ncol = 1)
```

### Relabund vs. activity
```{r}
gen_calc_data %>%
  filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = rel_amount, 
      y = u_d, 
      color = inc_time_d_str, 
      label = compound)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE,
              formula = "y~x") +
  geom_line(aes(group = compound), 
            color = "black", 
            alpha = 0.3) +
  geom_text_repel(size = 3) +
  theme_classic() +
  scale_color_npg() +
  labs(x = "Relative Amount",
       y = "Turnover (d^-1)",
       color = "Incubation Time") +
  theme(legend.position = "top")
```

### Relabund vs. activity colored by 2F

```{r}
gen_calc_data %>%
  filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = rel_amount, 
      y = u_d, 
      color = as.numeric(f_t), 
      label = compound)) +
  geom_point(aes(shape = inc_time_d_str)) +
  geom_smooth(method = "lm",
              se = FALSE,
              formula = "y~x") +
  geom_line(aes(group = compound), 
            color = "black", 
            alpha = 0.3) +
  geom_text_repel(color = "black", 
                  size = 3) +
  scale_color_viridis_c(option = "magma") +
  theme_classic() +
  labs(x = "Relative Amount",
       y = "Turnover (d^-1)",
       shape = "Incubation Time",
       color = "2F") +
  theme(legend.position = "bottom")
```
